{\small} High Performance P$^{3}$M N-body code: CUBEP3M

### 2012-06-11 Halos.tex
Included force tests over 10 steps
included predictions for bias

A second test of the accuracy of the halo finder algorithm is to extract the halo power spectrum $P_{h}(k)$ and compare the halo bias
with theoretical predictions. The halo bias is defined as $b(k) = \sqrt{P(k)/P_{h}(k)}$ and is shown in Fig. \ref{fig:halo}.
{\bf Expand here, describe, match with theory, etc...}
\begin{figure}%[ht]
%  \vskip -0.5cm 
  \begin{center}
    \includegraphics[width=3.2in]{graphs/bias.eps}
  \end{center}
  \caption{Halo bias, measured at $z=0$ from a $4000^3$ particles simulations with a side length of $3.2 h^{-1}$Gpc.
  Bottom to top curves correspond to haloes of different masses, from light to massive. The four bins are decades
  of halo masses; the first contains haloes made of 20-200 particles, the second of 200-2,000 and so on.
    \label{fig:halo}}
\end{figure}

>>>>

A second test of the accuracy of the halo finder algorithm is to extract the halo power spectrum $P_{h}(k)$ and compare the halo bias
with theoretical predictions. The halo bias is defined as $b(k) = \sqrt{P(k)/P_{h}(k)}$ and is shown in Fig. \ref{fig:halo}.
The results are organized in four mass bins, where the lowest mass consists of 20-200 particles, the second bin 
contains 200-2000 particles and so on. Comparisons with the linear predictions of \cite{Sheth_et_al} shows
results consistent findings of \cite{Thinker}, namely that low-mass bias is over-predicted and high-mass bias is under-predicted.

\begin{figure}%[ht]
%  \vskip -0.5cm 
  \begin{center}
    \includegraphics[width=3.2in]{graphs/bias.eps}
  \end{center}
  \caption{Halo bias, measured at $z=0$ from a RANGER4000 simulation with a side length of $3.2 h^{-1}$Gpc.
  Bottom to top curves correspond to haloes of different masses, from light to massive. The four bins are decades
  of halo masses; the first contains haloes made of 20-200 particles, the second of 200-2,000 and so on.
  The dashed lines are linear predictions from \protect \cite{Sheth_et_al}.
    \label{fig:halo}}
\end{figure}
